RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-14 paper.tex
arch. figure
yes

% What is the scope of our solution?

% We want our solution to play well with the rest of the ecosystem

@@

>>>>

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
systems for ...

% We want our solution to play well with the rest of the ecosystem
R has developed a complex ecosystem of compatible packages, software
tools and other resources. For example there are packages that make
it convenient to execute map-reduce programs, generate web interfaces,

@@

\begin{figure}
\hspace{-0.08\linewidth}
\includegraphics[width=1.1\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture}
\end{figure}
